\pagebreak
\section{Features}
The following features will make the Open-Source Software Database (OSSDB) a valuable
resource for the open-source software community.
The database will make it easier for software developers to find projects to
contribute to and for project maintainers to find contributors to help them build their
projects, while also providing valuable analytics and collaboration tools to aid
in the development process.


\subsection{Project Listings}
    The database will contain listings of:
    \begin{itemize}
        \item various open-source software projects,
        \item project descriptions,
        \item contributors,
        \item license types,
        \item most used programming languages.
    \end{itemize}

\subsection{Search}
The database will provide a search feature that allows users to easily search for open-source
software projects by name, keyword, domain, or any other relevant criteria.

\subsection{Filters}
The database will have filters to help users narrow down their search results based on
various criteria, such as project type, programming language, license type, and more.

\subsection{Contributions}
The database will allow contributors to easily contribute to open-source software projects
by providing contact information for project leads, instructions for getting involved, and more.

\subsection{User Profiles}
Users will be able to create profiles within the database that will track their
contributions, interests, and other relevant information.

\subsection{Notifications (under question)} 
The database will provide notifications to users regarding new software projects,
updates to existing projects, and other relevant events.

\subsection{Admin Panel}
The database will have an admin panel that will allow administrators to manage
project listings, user profiles, and other relevant aspects of the database.



