\pagebreak
\section{Requirements}

\begin{itemize}
    \item User Authentication: FOSSDB must provide user authentication to allow users to
    create and manage their profiles.

    \item Project creation: Registered users should be able to create projects and provide
    basic information about the project, such as project name, description, licenses,
    programming languages used, hosting platform, and operating systems supported.

    \item Star Rating: The FOSSDB must allow users to rate projects by assigning them stars.
    The rating system should be able to prevent multiple ratings from the same user.

    \item Tagging: FOSSDB should allow users to tag projects with relevant keywords
    to assist in searching and filtering.

    \item Licensing: FOSSDB should maintain a database of open source licenses and
    their associated details, including short name, full name, URL, and description.
    All projects listed in FOSSDB must be licensed under a FOSS license.
    Examples of FOSS licenses include the MIT License, the GNU General Public License (GPL),
    and the Apache License.

    \item Programming Languages: The FOSSDB should maintain a database of programming
    languages and their usage amount for each project.

    \item Hosting Platforms: The FOSSDB should maintain a database of hosting platforms
    and each project hosting platform associated URL.

    \item Operating Systems: The FOSSDB should maintain a database of operating systems and
    their associated details, including name, description, version.
\end{itemize}
