\pagebreak
\section{Introduction}
Open-source software has grown in popularity over the years due to its collaboration, innovation, and cost savings benefits.
Typically, open-source software is created and maintained by a community of developers who work together to improve their projects, share experiences and contribute to their growth.
As a result, there are now dozens of open source projects covering everything from software development to data science, robotics and more.

However, it can be difficult to keep track of all the open source projects available.
Project leaders and maintainers often struggle to find contributors to help build projects, while contributors struggle to find projects that match their interests and expertise.
This is where the Free and Open-Source Software Database (FOSSDB) comes into play.

The FOSSDB is a comprehensive online platform that acts as a central repository for tracking and managing open source projects.
This database provides project listings, search capabilities, filters, user profiles, etc. to help contributors find projects to contribute to
and for project leaders and maintainers to find contributors to help build the project.
The FOSSDB aims to provide a platform that fosters collaboration, transparency and innovation in the open-source software community.

The FOSSDB itself will be an open source project, and as such will be free and accessible to everyone.
This approach is in line with the open source philosophy, which encourages collaboration, transparency and community-driven innovation.
This project aims to encourage more people to get involved in open source projects and contribute to the growth of the community.
The project will rely on contributions and feedback from the community to continuously improve and refine the FOSSDB.
